\documentclass[10pt]{article}

\usepackage{amsfonts, amsmath, amssymb, amsthm}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Computation Documentation}
}

\allowdisplaybreaks
\delimitershortfall-1pt

\newcommand*\delimeter[3]{
	\ensuremath{\mathopen{}\left#2 #1\right#3\mathclose{}{\vphantom{\left#2 #1\right#3}}}
}

\newcommand*\pof[1]{\delimeter{#1}{(}{)}}
\newcommand*\sof[1]{\delimeter{#1}{[}{]}}
\newcommand*\cof[1]{\delimeter{#1}{\{}{\}}}
\newcommand*\aof[1]{\delimeter{#1}{\langle}{\rangle}}

\newcommand*\abs[1]{\delimeter{#1}{|}{|}}
\newcommand*\norm[1]{\delimeter{#1}{\|}{\|}}
\newcommand*\floor[1]{\delimeter{#1}{\lfloor}{\rfloor}}
\newcommand*\ceil[1]{\delimeter{#1}{\lceil}{\rceil}}

\newcommand*\ooint[1]{\delimeter{#1}{(}{)}}
\newcommand*\ocint[1]{\delimeter{#1}{(}{]}}
\newcommand*\coint[1]{\delimeter{#1}{[}{)}}
\newcommand*\ccint[1]{\delimeter{#1}{[}{]}}

\newcommand*\eval[1]{\delimeter{#1}{.}{|}}

\newcommand*\Dif{\ensuremath{\mathrm{D}}}
\newcommand*\dif{\ensuremath{\mathrm{d}}}
\newcommand*\Var{\ensuremath{\mathrm{Var}}}
\newcommand*\proj{\ensuremath{\mathrm{proj}}}

\begin{document}
	\pagestyle{empty}

	\section{Problem Setup}

	As input, we are given a directed (multi-)graph \(G = \pof{V_G, E_G}\), where each vertex \(s \in V_G \subseteq S^2\) is a geographic position, and each edge \(e = \pof{s, s'}\) has an associated (Olivier-Ricci) curvature \(R_e \in \ooint{-2, 1}\) and an associated latency \(t_e \in \mathbb{R}_{\ge 0}\).

	We want to return a surface in \(\mathbb{R}^3\) that is the graph of a function \(\rho : S^2 \to \mathbb{R}_{> 0}\) whose minimal geodesics \(g_e\) between \(\pof{s, \rho\pof{s}}\) and \(\pof{s', \rho\pof{s'}}\) have length \(\phi_e\) that is in a linear relationship with the latency.

	The strategy to realize this idea is to create a mesh \(M = \pof{V_M, E_M}\) supported on a subset of \(S^2\). We use a standard \href{https://en.wikipedia.org/wiki/Doubly_connected_edge_list}{half-edge} setup, so that \(E_M\) is a set of ordered pairs (edges are directed). Let \(P\) be the support. Then for each \(s_i \in P\), we want to assign a \(\rho_i \in \mathbb{R}_{> 0}\), which in turn gives a point \(v_i = \pof{s_i, \rho_i} \in V_M\). This setup is made explicit in \texttt{mesh/sphere.py}. Note that there is an assumption that if we project \(V_M\) onto \(S^2\), then that set contains \(V_G\). In practice, we can just use a fine enough mesh and map the vertices in \(V_G\) to their nearest projections.

	A similar setup is found in \texttt{mesh/rectangle.py}, where we use \(\ccint{0, 1}^2\) instead of \(S^2\). In general, this setup just requires that the position of any mesh vertex is controlled by a single scalar parameter.

	\section{Objective/Loss Functions}

	To enforce that the mesh approximates our desired surface, we roughly\footnote{The actual definitions are scaled so that the values are comparable regardless of the choice of mesh.} define the objective functions \begin{align*}
		\mathcal{L}_{\mathrm{geodesic}}\pof{M} &\triangleq \sum_{e \in E_G} \pof{\text{least squares residual of edge \(e\)}}^2, \\
		\mathcal{L}_{\mathrm{smooth}}\pof{M} &\triangleq -\rho^\intercal L_C^{\text{N}}\rho, \\
		\mathcal{L}_{\mathrm{curvature}}\pof{M} &\triangleq \sum_{\substack{v \in V_M \\ e \in E_G \\ \text{\(v\) close to \(e\)}}} \pof{\kappa\pof{v} - R_e}^2, \\
		\mathcal{L}\pof{M} &\triangleq \lambda_{\mathrm{geodesic}}\mathcal{L}_{\mathrm{geodesic}}\pof{M} + \lambda_{\mathrm{curvature}}\mathcal{L}_{\mathrm{curvature}}\pof{M} + \lambda_{\mathrm{smooth}}\mathcal{L}_{\mathrm{smooth}}\pof{M},
	\end{align*} where the \(\lambda\)'s are tunable hyperparameters. The other variables will be defined in the upcoming subsections. Our goal is then to minimize \(\mathcal{L}\pof{M}\).

	Note that the loss functions (particularly the geodesic and total ones) also have a dependence on the measured latencies. We omit that as a written parameter because they are treated as fixed (we are really optimizing over the manifold, not over the measured latencies).

	\subsection{Laplacian}
	\input{laplacian.tex}

	\subsection{Geodesic Distance via the Heat Method}
	\input{geodesic_distance.tex}

	\subsection{Geodesic Loss}
	\input{geodesic_loss.tex}

	\subsection{Smoothness Loss}
	\input{smoothness_loss.tex}

	\subsection{Curvature Loss}
	\input{curvature_loss.tex}
\end{document}
